TacticToe: Learning to Prove with Tactics

### 2018-02-19 tactictoe_jv.tex
Tweaks and fix some English

\paragraph{Goals and theorems.}
A goal is represented as a sequent. Each sequent is composed of
a list of assumptions and a conclusion which are higher-order logic formulas.
When a goal is proven, it becomes a theorem. And if the developer gives it a
name then we refer to it as a top-level theorem.

@@

\paragraph{Tactics in \holfour.}
Considering concrete implementation details now, a \emph{tactic} is a function
that takes a goal (or proof obligation) and returns a list of goals (subgoals 
of the original goal) together
with a validation function.
Calling the validation function on a list of \emph{theorems}, corresponding to 
the list of subgoals, results in a theorem corresponding to the original goal.
For example, if the list of subgoals is empty, then calling the validation 
function on the empty list yields the originally goal sequent as a theorem.
In this way, tactics implement the plumbing of backwards, goal-directed, proof 
construction. 
Because validation functions are only important to check the final proof, we 
omit them during the description of proof search algorithm. We denote $t(g)$ 
the lists of goals produced by the application of a tactic $t$ to a goal 
$g$.

@@

The application of tactic to an initial conjecture produces a list of goals. 
Each of the created goals can in turn be the input other tactics. Moreover, it 
is possible to try multiple tactics on the same goal. In order to keep track of 
the progress made so far from the initial conjecture we want to solve, we 
organize goals and tactics into a graph with list of goals as nodes and tactics 
as edges (See Definition~\ref{def:stree}).

In this section, we only give a description of the graph at a given 
moment of the search after a certain amount of tactic applications. 
The exploration of the tree is decided by MCTS algorithm in 
Section~\ref{sec:proofsearch}, which is guided by a prediction algorithms 
presented in Section~\ref{sec:predictions}.

@@

%A similar trade-off between exploration and exploitation exists in algorithm
%like Monte Carlo. However, Monte Carlo tree search metrics are based on many
%simulations and do not reflect our exploration strategy that only
\paragraph{Node selection}
Through node extension steps the search tree grows and the number of paths to
explore increases. To decide which node to extend next, a evolving value for
each node is given in Definition~\ref{def:value}. The algorithm that performs
node selection starts from the root of the search tree. From the current node,
the function \texttt{CompareChildren} chooses among the children of its open 
goal the one with the highest value.

>>>>

\paragraph{Goals and theorems.}
A goal is represented as a \emph{sequent}.
A sequent is composed of a set of assumptions and a conclusion, all of which are higher-order logic formulas.
When a goal is proven, it becomes a theorem.
If the developer gives the theorem a name then we refer to it as a top-level theorem.

@@

\paragraph{Tactics in \holfour.}
Considering concrete implementation details now, a \emph{tactic} is a function
that takes a goal (or proof obligation) and returns a list of goals (subgoals
of the original goal) together
with a validation function.
Calling the validation function on a list of \emph{theorems}, corresponding to
the list of subgoals, results in a theorem corresponding to the original goal.
For example, if the list of subgoals is empty, then calling the validation
function on the empty list yields the originally goal sequent as a theorem.
In this way, tactics implement the plumbing of backwards, goal-directed, proof
construction.
Because validation functions are only important to check the final proof, we
omit them during the description of proof search algorithm. We denote by $t(g)$
the list of goals produced by the application of a tactic $t$ to a goal $g$.

@@

The application of a tactic to an initial conjecture produces a list of goals.
Each of the created goals can in turn be the input to other tactics.
Moreover, it is possible to try multiple tactics on the same goal.
In order to keep track of the progress made so far from the initial conjecture we want to solve, we organize goals and tactics into a graph with list of goals as nodes and tactics as edges (See Definition~\ref{def:stree}).

In this section, we only give a description of the graph at a given
moment of the search after a certain amount of tactic applications.
Exploration of the tree is directed by the MCTS algorithm in
Section~\ref{sec:proofsearch}, which is guided by prediction algorithms
presented in Section~\ref{sec:predictions}.

@@

%A similar trade-off between exploration and exploitation exists in algorithm
%like Monte Carlo. However, Monte Carlo tree search metrics are based on many
%simulations and do not reflect our exploration strategy that only
\paragraph{Node selection}
Through node extension steps the search tree grows and the number of paths to
explore increases. To decide which node to extend next, a evolving value for
each node is given in Definition~\ref{def:value}. The algorithm that performs
node selection starts from the root of the search tree. From the current node,
the function \texttt{CompareChildren} choses among the children of its open
goal the one with the highest value.
